Nanophotonic Computational Design

### 2013-03-14 paper/paper.tex
a
Working on paper...

\subsection{TE mode converter}
Our first result was a mode conversion device operating in the TE polarization,
    which we define as that mode where the primary E-field component
    of the waveguide mode is polarized in the plane of the structure.

@@

@@

>>>>

\subsection{TE mode converter}
Our first result was a mode conversion device operating in the TE polarization,
    which we define as that mode where the primary E-field component
    of the waveguide mode is polarized in the plane of the structure.
Such a device is significant because 
    it demonstrates the feasibility of muli-mode on-chip optical networks
    by showing that high-efficiency mode conversion 
    can readily be achieved in planar on-chip nanophotonic structures.
Furthermore, this device also demonstrates that this can be achieved
    within very small device footprints 
    ($1.6 \times 2.4$ microns for this device in particular).

@@

The performance of the device is shown in \fig{takeaway}.
The conversion efficiency into the second-order mode is lower
    than desired (86.4\% as opposed to 90\% to 100\%);
    this may be due to evanescent modes ``interfering'' 
    with the output field overlap calculation.

@@

\subsection{TM mode converter}

In addition to mode conversion in the TE polarization (E-field in-plane),
    we show that TM polarization (E-field out-of-plane) mode converters
    can be designed as well.
This example shows that full three-dimensional structures 
    truly are possible,
    and that no approximations are needed for our method.

Since our method is design-by-specification, 
    the design of a TM mode converter requires only
    a small modification to the performance specification of the device;
    namely the polarization of the input and output modes (\fig{wgc_tm}).
Specifically, we still design for 
    $\ge 90\%$ conversion into the second-order mode and 
    a $\le 1\%$ allowance for the fundamental mode to be transmitted.

\myfig{3Db_wgc_tm}
    {Perfomance specification of the TM mode converter.
    Input mode is the fundamental TM-polarized mode on the left.
    Primary output mode is the second-order mode on the right.
    Output power in the transmitted fundamental mode on the right 
    above 1\% is to be rejected.
    The structure shown is the final three-dimensional design.}

The performance of the device is shown in \fig{wgc_tm}.
The lower conversion efficiency of 76.9\% in contrast to the TE mode converter
    may be attributed to the lower confinement of the TM waveguide modes.
However, good rejection of only 1\% is still achieved.

\myfig{wgc_tm}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 76.9\%,
    while the power into the rejection mode (fundamental) is 1.0\%.}

\subsection{Spatial, polarization, and wavelength splitters}
Next, we demonstrate the design of nanophotonic waveguide mode splitters.
Such devices can be used as multiplexors or demultiplexors and
    are the key component in utilizing a single waveguide to transmit 
    multiple optical signals.

As a demonstration of the versatility of our method, 
    we show that it is capable of designing mode splitting devices 
    based on either the spatial profile, the polarization, or the wavelength
    of the input modes.
